---
title: "A Visual Look at Stack Overflow's Question Tags"
author: "Max Woolf (@minimaxir)"
date: "2017-02-09"
output:
  html_notebook:
    highlight: tango
    mathjax: null
    number_sections: yes
    theme: spacelab
---

This R Notebook is the complement to my blog post [A Visual Overview of Stack Overflow's Question Tags](http://minimaxir.com/2018/02/stack-overflow-questions/).

This notebook is licensed under the MIT License. If you use the code or data visualization designs contained within this notebook, it would be greatly appreciated if proper attribution is given back to this notebook and/or myself. Thanks! :)

# Setup

```{r}
library(tidyverse)
library(scales)
library(viridis)

source("bb_court_college.R")

sessionInfo()
```

```{r}
theme_set(theme_minimal(base_size=9, base_family="Source Sans Pro") +
            theme(plot.title = element_text(size=8, family="Source Sans Pro Bold", margin=margin(t = -0.1, b = 0.1, unit='cm')),
                  axis.title.x = element_text(size=8),
                  axis.title.y = element_text(size=8),
                  plot.subtitle = element_text(family="Source Sans Pro Semibold", color="#969696", size=6),
                  plot.caption = element_text(size=6, color="#969696"),
                  legend.text = element_text(size = 6),
                  legend.key.width = unit(0.25, unit='cm')))

bb_theme <- theme(
                plot.title = element_text(size=10, family="Source Sans Pro Bold", margin=margin(t = -0.1, b = 0.0, unit='cm')),
                axis.title.x = element_blank(),
                axis.title.y = element_blank(),
                axis.text.x = element_blank(),
                axis.text.y = element_blank(),
                panel.grid = element_blank(),
                legend.position = 'top',
                legend.text = element_text(size = 6),
                legend.title = element_text(size = 6),
                legend.key.width = unit(1, unit='cm'),
                legend.key.height = unit(0.25, unit='cm'),
                legend.margin = margin(c(0, 0, -0.4, 0), unit='cm'))
```

```{r}
file_path <- "court.csv"
df <- read_csv(file_path)
df %>% head()
```

BigQuery:

```{sql eval=FALSE, include=TRUE}
#standardSQL
SELECT CAST(event_coord_x as int64) as x,
        600 - CAST(event_coord_y as int64) as y,
        COUNT(*) as attempts,
        COUNTIF(points_scored IS NOT NULL) as successes,
        AVG(IFNULL(CAST(points_scored as int64), 0)) as avg_points
FROM `bigquery-public-data.ncaa_basketball.mbb_pbp_sr`
WHERE shot_type IS NOT NULL
AND event_coord_x IS NOT NULL
AND event_coord_y IS NOT NULL
GROUP BY x, y
ORDER BY attempts DESC, avg_points DESC
```

```{r}
df <- df %>% mutate(
  x = rescale(x, to = c(0,94)),
  y = rescale(y, to = c(-50,0)),
  perc_success = successes/attempts
)

df %>% head()
```

```{r}
plot <- P_180 +
          stat_summary_2d(data=df, aes(x=x, y=y, z=attempts), alpha=0.8, binwidth=c(25/(2*25), 50/(2*47)), fun=sum) +
          scale_fill_viridis(option='inferno', end=1, labels=comma) +
          labs(title=sprintf('Heat Map of %s Basketball Shots from NCAA Games', df %>% pull(attempts) %>% sum() %>% comma()),
                subtitle='Starting with the 2013-14 season. Via Sportradar data located in BigQuery',
               fill='# of 2pt/3pt Shot Attempts\nMade From Spot',
               caption = "Max Woolf — minimaxir.com") +
          bb_theme

ggsave('ncaa_count_attempts_unlog.png', plot, width=6, height=4)
```

```{r}
plot <- P_180 +
          stat_summary_2d(data=df, aes(x=x, y=y, z=attempts), alpha=0.8, binwidth=c(25/(2*25), 50/(2*47)), fun=sum) +
          scale_fill_viridis(option='inferno', end=1, labels=comma, trans='log10') +
          labs(title=sprintf('Heat Map of %s Basketball Shots from NCAA Games', df %>% pull(attempts) %>% sum() %>% comma()),
                subtitle='Starting with the 2013-14 season. Via Sportradar data located in BigQuery',
               fill='# of 2pt/3pt Shot Attempts\nMade From Spot',
               caption = "Max Woolf — minimaxir.com") +
          bb_theme

ggsave('ncaa_count_attempts.png', plot, width=6, height=4)
```

```{r}
plot <- P_180 +
          stat_summary_2d(data=df, aes(x=x, y=y, z=perc_success), alpha=0.8, binwidth=c(25/(2*25), 50/(2*47)), fun=mean, drop=T) +
          scale_fill_viridis(option='viridis', end=1, label=percent) +
          labs(title=sprintf('Average Points Earned From of %s Basketball Shots from NCAA Games', df %>% pull(attempts) %>% sum() %>% comma()),
                subtitle='Starting with the 2013-14 season. Via Sportradar data located in BigQuery',
               fill='Average Points Earned From Shot Attempts\nMade From Spot',
               caption = "Max Woolf — minimaxir.com") +
          bb_theme

ggsave('ncaa_count_perc_success.png', plot, width=6, height=4)
```

```{r}
plot <- P_180 +
          stat_summary_2d(data=df, aes(x=x, y=y, z=avg_points), alpha=0.8, binwidth=c(25/(2*25), 50/(2*47)), fun=mean, drop=T) +
          scale_fill_viridis(option='viridis', end=1) +
          labs(title=sprintf('Average Points Earned From of %s Basketball Shots from NCAA Games', df %>% pull(attempts) %>% sum() %>% comma()),
                subtitle='Starting with the 2013-14 season. Via Sportradar data located in BigQuery',
               fill='Average Points Earned From Shot Attempts\nMade From Spot',
               caption = "Max Woolf — minimaxir.com") +
          bb_theme

ggsave('ncaa_count_avg_points.png', plot, width=6, height=4)
```


## Half Court

Query:

```{sql eval=FALSE, include=TRUE}
#standardSQL
SELECT IF(event_coord_x < 564, CAST(event_coord_x as int64), 1128 - CAST(event_coord_x as int64)) as x,
        IF(event_coord_x < 564, 600 - CAST(event_coord_y as int64), CAST(event_coord_y as int64)) as y,
        COUNT(*) as attempts,
        COUNTIF(points_scored IS NOT NULL) as successes, 
        AVG(IFNULL(CAST(points_scored as int64), 0)) as avg_points
FROM `bigquery-public-data.ncaa_basketball.mbb_pbp_sr`
WHERE shot_type IS NOT NULL
AND event_coord_x IS NOT NULL
AND event_coord_y IS NOT NULL
AND IF(event_coord_x < 564, 'left', 'right') = team_basket
GROUP BY x, y
ORDER BY attempts DESC, avg_points DESC
```


```{r}
file_path_half <- "half_court.csv"
df_half <- read_csv(file_path_half)
df_half %>% head()
```

```{r}
df_half <- df_half %>% mutate(
  x = rescale(x, to = c(0, 47)),
  y = rescale(y, to = c(0, 50)),
  perc_success = successes/attempts
)

df_half %>% head()
```

```{r}
plot <- P_half +
          stat_summary_2d(data=df_half, aes(x=y, y=x, z=attempts), alpha=0.8, bins=100, fun=sum) +
          scale_fill_viridis(option='inferno', end=1, labels=comma, trans='log10') +
          labs(title=sprintf('Heat Map of %s Basketball Shots from NCAA Games', df_half %>% pull(attempts) %>% sum() %>% comma()),
                subtitle='Starting with the 2013-14 season. Via Sportradar data located in BigQuery',
               fill='# of 2pt/3pt Shot Attempts\nMade From Spot',
               caption = "Max Woolf — minimaxir.com") +
          bb_theme

ggsave('ncaa_count_attempts_half_log.png', plot, width=4, height=4)
```


## Half Court, Faceted by Type of Shot

BigQuery:

```{sql eval=FALSE, include=TRUE}
#standardSQL
SELECT shot_type,
        IF(event_coord_x < 564, CAST(event_coord_x as int64), 1128 - CAST(event_coord_x as int64)) as x,
        IF(event_coord_x < 564, 600 - CAST(event_coord_y as int64), CAST(event_coord_y as int64)) as y,
        COUNT(*) as attempts,
        COUNTIF(points_scored IS NOT NULL) as successes, 
        AVG(IFNULL(CAST(points_scored as int64), 0)) as avg_points
FROM `bigquery-public-data.ncaa_basketball.mbb_pbp_sr`
WHERE shot_type IS NOT NULL
AND event_coord_x IS NOT NULL
AND event_coord_y IS NOT NULL
AND IF(event_coord_x < 564, 'left', 'right') = team_basket
GROUP BY shot_type, x, y
ORDER BY attempts DESC, avg_points DESC
```


```{r}
file_path_half_types <- "half_types.csv"
df_half_types <- read_csv(file_path_half_types)
df_half_types %>% head()
```

```{r}
df_half_types <- df_half_types %>% mutate(
  x = rescale(x, to = c(0, 47)),
  y = rescale(y, to = c(0, 50)),
  perc_success = successes/attempts
)

df_half_types %>% head()
```


```{r}
plot <- P_half +
          stat_summary_2d(data=df_half_types, aes(x=y, y=x, z=attempts), alpha=0.8, bins=100, fun=sum) +
          scale_fill_viridis(option='inferno', end=1, labels=comma, trans='log10') +
          facet_wrap(~ shot_type, ncol=2) +
          labs(title=sprintf('Heat Map of %s Basketball Shots from NCAA Games', df_half_types %>% pull(attempts) %>% sum() %>% comma()),
                subtitle='Starting with the 2013-14 season. Via Sportradar data located in BigQuery',
               fill='# of 2pt/3pt Shot Attempts\nMade From Spot',
               caption = "Max Woolf — minimaxir.com") +
          bb_theme

ggsave('ncaa_count_attempts_half_types_log.png', plot, width=3, height=5)
```

## Half Court, Faceted by 10 Minute Time Buckets.

```{sql eval=FALSE, include=TRUE}
#standardSQL
SELECT IF(elapsed_time_sec >= 60*40, 99, CAST(FLOOR(elapsed_time_sec/300) AS int64)) as min_interval,
        IF(event_coord_x < 564, CAST(event_coord_x as int64), 1128 - CAST(event_coord_x as int64)) as x,
        IF(event_coord_x < 564, 600 - CAST(event_coord_y as int64), CAST(event_coord_y as int64)) as y,
        COUNT(*) as attempts,
        COUNTIF(points_scored IS NOT NULL) as successes, 
        AVG(IFNULL(CAST(points_scored as int64), 0)) as avg_points
FROM `bigquery-public-data.ncaa_basketball.mbb_pbp_sr`
WHERE shot_type IS NOT NULL
AND event_coord_x IS NOT NULL
AND event_coord_y IS NOT NULL
AND IF(event_coord_x < 564, 'left', 'right') = team_basket
GROUP BY min_interval, x, y
ORDER BY attempts DESC, avg_points DESC
```

```{r}
file_path_half_interval <- "half_interval.csv"
df_half_interval <- read_csv(file_path_half_interval)
df_half_interval %>% head()
```

```{r}
interval_levels = c('1st\n20:00 — 15:00',
                    '1st\n14:59 — 10:00',
                    '1st\n09:59 — 05:00',
                    '1st\n04:59 — 00:00',
                    '2nd\n20:00 — 15:00',
                    '2nd\n14:59 — 10:00',
                    '2nd\n09:59 — 05:00',
                    '2nd\n04:59 — 00:00',
                    'OT')


df_half_interval <- df_half_interval %>% mutate(
  x = rescale(x, to = c(0, 47)),
  y = rescale(y, to = c(0, 50)),
  perc_success = successes/attempts,
  min_interval = factor(min_interval, labels = interval_levels)
)

df_half_interval %>% head()
```

```{r}
plot <- P_half +
          stat_summary_2d(data=df_half_interval, aes(x=y, y=x, z=attempts), alpha=0.8, bins=25, fun=sum) +
          scale_fill_viridis(option='inferno', end=1, labels=comma, trans='log10') +
          facet_grid(min_interval ~ shot_type) +
          labs(title=sprintf('Heat Map of %s Basketball Shots from NCAA Games', df %>% pull(attempts) %>% sum() %>% comma()),
                subtitle='Starting with the 2013-14 season. Via Sportradar data located in BigQuery',
               fill='# of 2pt/3pt Shot Attempts\nMade From Spot',
               caption = "Max Woolf — minimaxir.com") +
          bb_theme

ggsave('ncaa_count_attempts_half_interval_log.png', plot, width=4, height=7)
```

## Half Court, by Point Delta at Time of Shot

BigQuery:

```{sql eval=FALSE, include=TRUE}
#standardSQL
SELECT CASE WHEN score_delta < -20 THEN '<-20'
            WHEN score_delta >= -20 AND score_delta < -10 THEN '-20 — -11'
            WHEN score_delta >= -10 AND score_delta < 0 THEN '-10 — -1'
            WHEN score_delta = 0 THEN '0'
            WHEN score_delta >= 1 AND score_delta <= 10 THEN '1 — 10'
            WHEN score_delta > 10 AND score_delta <= 20 THEN '11 — 20'
            WHEN score_delta > 20  THEN '>20'
            END
            AS score_delta_interval,
        shot_type,
        IF(event_coord_x < 564, CAST(event_coord_x as int64), 1128 - CAST(event_coord_x as int64)) as x,
        IF(event_coord_x < 564, 600 - CAST(event_coord_y as int64), CAST(event_coord_y as int64)) as y,
        COUNT(*) as attempts,
        COUNTIF(points_scored IS NOT NULL) as successes, 
        AVG(IFNULL(CAST(points_scored as int64), 0)) as avg_points
FROM (
SELECT *, team_score - (game_score - team_score) as score_delta
  FROM (
    SELECT event_coord_x, event_coord_y, points_scored, shot_type, team_basket,
    SUM(IFNULL(CAST(points_scored as int64), 0)) OVER (PARTITION BY game_id, team_id ORDER BY timestamp) - IFNULL(CAST(points_scored as int64), 0) as team_score,
    SUM(IFNULL(CAST(points_scored as int64), 0)) OVER (PARTITION BY game_id ORDER BY timestamp) - IFNULL(CAST(points_scored as int64), 0) as game_score
    FROM `bigquery-public-data.ncaa_basketball.mbb_pbp_sr`
  )
)
WHERE shot_type IS NOT NULL
AND event_coord_x IS NOT NULL
AND event_coord_y IS NOT NULL
AND IF(event_coord_x < 564, 'left', 'right') = team_basket
GROUP BY score_delta_interval, shot_type, x, y
ORDER BY attempts DESC, avg_points DESC
```

```{r}
file_path_half_score <- "half_score.csv"
df_half_score <- read_csv(file_path_half_score)
df_half_score %>% head()
```

```{r}
score_levels <- c('<-20', '-20 — -11', '-10 — -1', '0', '1 — 10', '11 — 20', '>20')

df_half_score <- df_half_score %>% mutate(
  x = rescale(x, to = c(0, 47)),
  y = rescale(y, to = c(0, 50)),
  perc_success = successes/attempts,
  score_delta_interval = factor(score_delta_interval, levels = score_levels)
)

df_half_score %>% head()
```

```{r}
plot <- P_half +
          stat_summary_2d(data=df_half_score, aes(x=y, y=x, z=attempts), alpha=0.8, bins=25, fun=sum) +
          scale_fill_viridis(option='inferno', end=1, labels=comma, trans='log10') +
          facet_grid(score_delta_interval ~ shot_type) +
          labs(title=sprintf('Heat Map of %s Basketball Shots from NCAA Games', df_half_score %>% pull(attempts) %>% sum() %>% comma()),
                subtitle='Starting with the 2013-14 season. Via Sportradar data located in BigQuery',
               fill='# of 2pt/3pt Shot Attempts\nMade From Spot',
               caption = "Max Woolf — minimaxir.com") +
          bb_theme

ggsave('ncaa_count_attempts_half_score_log.png', plot, width=3, height=4)
```

## Bar Chart of Shot Types

```{r}
df_half_types_agg <- df_half_types %>%
                        group_by(shot_type) %>%
                        summarize(total_attempts = sum(attempts),
                                  total_successes = sum(successes),
                                  perc_success = total_successes/total_attempts,
                                  avg_points = mean(avg_points)) %>%
                        ungroup() %>%
                        mutate(prop_attempts = total_attempts/sum(total_attempts)) %>%
                        arrange(desc(total_attempts)) 

df_half_types_agg$shot_type <- factor(df_half_types_agg$shot_type, levels=rev(df_half_types_agg$shot_type))
```

```{r}
plot <- ggplot(df_half_types_agg, aes(x=shot_type, y=prop_attempts, fill=shot_type, color=shot_type)) +
          geom_bar(stat="identity", color=NA) +
          geom_text(aes(label=sprintf('%0.1f%%', prop_attempts*100)), size=3, family="Source Sans Pro Bold", hjust=-0.25) +
          coord_flip() +
          scale_color_brewer(palette="Set1", guide=F) +
          scale_fill_brewer(palette="Set1", guide=F) +
          scale_y_continuous(labels=percent, limits=c(0,1)) +
          labs(title=sprintf('Proportion of %s Basketball Shots by Type from NCAA Games', df_half_types_agg %>% pull(total_attempts) %>% sum() %>% comma()),
                subtitle='Starting with the 2013-14 season. Via Sportradar data located in BigQuery',
               caption = "Max Woolf — minimaxir.com",
               y = "Proportion of Shot Attempts Made") +
          theme(axis.title.y = element_blank())

ggsave('ncaa_types_prop_attempts.png', plot, width=4, height=2)
```

```{r}
plot <- ggplot(df_half_types_agg, aes(x=shot_type, y=perc_success, fill=shot_type)) +
          geom_bar(stat="identity") +
          geom_text(aes(label=sprintf('%0.1f%%', perc_success*100)), size=3, color="white", family="Source Sans Pro Bold", hjust=1.25) +
          coord_flip() +
          scale_fill_brewer(palette="Set1", guide=F) +
          scale_y_continuous(labels=percent, limits=c(0,1)) +
          labs(title=sprintf('Shot Success of %s Basketball Shots by Type from NCAA Games', df_half_types_agg %>% pull(total_attempts) %>% sum() %>% comma()),
                subtitle='Starting with the 2013-14 season. Via Sportradar data located in BigQuery',
               caption = "Max Woolf — minimaxir.com",
               y = "% of Successful Shots Made by Type") +
          theme(axis.title.y = element_blank())

ggsave('ncaa_types_perc.png', plot, width=4, height=2)
```


## Bar Charts of Elapsed Time, Faceted by Shot Type

```{r}
df_half_interval_agg <- df_half_interval %>%
                        group_by(min_interval, shot_type) %>%
                        summarize(total_attempts = sum(attempts),
                                  total_successes = sum(successes),
                                  perc_success = total_successes/total_attempts,
                                  avg_points = mean(avg_points)) %>%
                        arrange(desc(perc_success))  %>%
                        ungroup() %>%
                        group_by(min_interval) %>%
                        mutate(prop_attempts = total_attempts/sum(total_attempts)) %>%
                        arrange(desc(total_attempts)) 

df_half_interval_agg$shot_type <- factor(df_half_interval_agg$shot_type, levels=rev(df_half_types_agg$shot_type))
```

```{r}
plot <- ggplot(df_half_interval_agg, aes(x=shot_type, y=perc_success, fill=shot_type)) +
          geom_bar(stat="identity") +
          geom_text(aes(label=sprintf('%0.1f%%', perc_success*100)), size=2, color="white", family="Source Sans Pro Bold", hjust=1.05) +
          coord_flip() +
          facet_wrap(~ min_interval) +
          scale_fill_brewer(palette="Set1", guide=F) +
          scale_y_continuous(labels=percent, limits=c(0,1)) +
          labs(title=sprintf('Shot Success of %s Basketball Shots by Type from NCAA Games', df_half_interval_agg %>% pull(total_attempts) %>% sum() %>% comma()),
                subtitle='Starting with the 2013-14 season. Via Sportradar data located in BigQuery',
               caption = "Max Woolf — minimaxir.com",
               y = "% of Successful Shots Made by Type") +
          theme(axis.title.y = element_blank())

ggsave('ncaa_types_perc_success_type_elapsed.png', plot, width=4, height=4)
```

```{r}
plot <- ggplot(df_half_interval_agg, aes(x=shot_type, y=prop_attempts, fill=shot_type, color=shot_type)) +
          geom_bar(stat="identity", color=NA) +
          geom_text(aes(label=sprintf('%0.1f%%', prop_attempts*100)), size=2, family="Source Sans Pro Bold", hjust=-0.25) +
          coord_flip() +
          facet_wrap(~ min_interval) +
          scale_color_brewer(palette="Set1", guide=F) +
          scale_fill_brewer(palette="Set1", guide=F) +
          scale_y_continuous(labels=percent, limits=c(0,1)) +
          labs(title=sprintf('Proportion of %s Basketball Shots by Type from NCAA Games', df_half_interval_agg %>% pull(total_attempts) %>% sum() %>% comma()),
                subtitle='Starting with the 2013-14 season. Via Sportradar data located in BigQuery',
               caption = "Max Woolf — minimaxir.com",
               y = "Proportion of Shot Attempts Made") +
          theme(axis.title.y = element_blank())

ggsave('ncaa_types_prop_type_elapsed.png', plot, width=4, height=4)
```

## Bar Charts of Score Delta, Faceted by Shot Type

```{r}
df_half_score_agg <- df_half_score %>%
                        group_by(score_delta_interval, shot_type) %>%
                        summarize(total_attempts = sum(attempts),
                                  total_successes = sum(successes),
                                  perc_success = total_successes/total_attempts,
                                  avg_points = mean(avg_points)) %>%
                        arrange(desc(perc_success))  %>%
                        ungroup() %>%
                        group_by(score_delta_interval) %>%
                        mutate(prop_attempts = total_attempts/sum(total_attempts)) %>%
                        arrange(desc(total_attempts)) 

df_half_score_agg$shot_type <- factor(df_half_score_agg$shot_type, levels=rev(df_half_types_agg$shot_type))
```

```{r}
plot <- ggplot(df_half_score_agg, aes(x=shot_type, y=perc_success, fill=shot_type)) +
          geom_bar(stat="identity") +
          geom_text(aes(label=sprintf('%0.1f%%', perc_success*100)), size=2, color="white", family="Source Sans Pro Bold", hjust=1.05) +
          coord_flip() +
          facet_wrap(~ score_delta_interval) +
          scale_fill_brewer(palette="Set1", guide=F) +
          scale_y_continuous(labels=percent, limits=c(0,1)) +
          labs(title=sprintf('Shot Success of %s Basketball Shots by Type from NCAA Games', df_half_interval_agg %>% pull(total_attempts) %>% sum() %>% comma()),
                subtitle='Starting with the 2013-14 season. Via Sportradar data located in BigQuery',
               caption = "Max Woolf — minimaxir.com",
               y = "% of Successful Shots Made by Type") +
          theme(axis.title.y = element_blank())

ggsave('ncaa_types_perc_success_type_score.png', plot, width=4, height=4)
```

```{r}
plot <- ggplot(df_half_score_agg, aes(x=shot_type, y=prop_attempts, fill=shot_type, color=shot_type)) +
          geom_bar(stat="identity", color=NA) +
          geom_text(aes(label=sprintf('%0.1f%%', prop_attempts*100)), size=2, family="Source Sans Pro Bold", hjust=-0.25) +
          coord_flip() +
          facet_wrap(~ score_delta_interval) +
          scale_color_brewer(palette="Set1", guide=F) +
          scale_fill_brewer(palette="Set1", guide=F) +
          scale_y_continuous(labels=percent, limits=c(0,1)) +
          labs(title=sprintf('Proportion of %s Basketball Shots by Type from NCAA Games', df_half_interval_agg %>% pull(total_attempts) %>% sum() %>% comma()),
                subtitle='Starting with the 2013-14 season. Via Sportradar data located in BigQuery',
               caption = "Max Woolf — minimaxir.com",
               y = "Proportion of Shot Attempts Made by Type") +
          theme(axis.title.y = element_blank())

ggsave('ncaa_types_prop_type_score.png', plot, width=4, height=4)
```

# LICENSE

The MIT License (MIT)

Copyright (c) 2018 Max Woolf

Permission is hereby granted, free of charge, to any person obtaining a copy of this software and associated documentation files (the "Software"), to deal in the Software without restriction, including without limitation the rights to use, copy, modify, merge, publish, distribute, sublicense, and/or sell copies of the Software, and to permit persons to whom the Software is furnished to do so, subject to the following conditions:

The above copyright notice and this permission notice shall be included in all copies or substantial portions of the Software.

THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE SOFTWARE.