---
title: "A Visual Look at Stack Overflow's Question Tags"
author: "Max Woolf (@minimaxir)"
date: "2017-02-09"
output:
  html_notebook:
    highlight: tango
    mathjax: null
    number_sections: yes
    theme: spacelab
---

This R Notebook is the complement to my blog post [A Visual Overview of Stack Overflow's Question Tags](http://minimaxir.com/2018/02/stack-overflow-questions/).

This notebook is licensed under the MIT License. If you use the code or data visualization designs contained within this notebook, it would be greatly appreciated if proper attribution is given back to this notebook and/or myself. Thanks! :)

# Setup

```{r}
library(tidyverse)
library(lubridate)
library(scales)
library(viridis)

source("bb_court_college.R")

sessionInfo()
```

```{r}
theme_set(theme_minimal(base_size=9, base_family="Source Sans Pro") +
            theme(plot.title = element_text(size=8, family="Source Sans Pro Bold", margin=margin(t = -0.1, b = 0.1, unit='cm')),
                  axis.title.x = element_text(size=8),
                  axis.title.y = element_text(size=8),
                  plot.subtitle = element_text(family="Source Sans Pro Semibold", color="#969696", size=6),
                  plot.caption = element_text(size=6, color="#969696"),
                  legend.text = element_text(size = 6),
                  legend.key.width = unit(0.25, unit='cm')))

bb_theme <- theme(
                plot.title = element_text(size=10, family="Source Sans Pro Bold", margin=margin(t = -0.1, b = 0.0, unit='cm')),
                axis.title.x = element_blank(),
                axis.title.y = element_blank(),
                axis.text.x = element_blank(),
                axis.text.y = element_blank(),
                panel.grid = element_blank(),
                legend.position = 'top',
                legend.text = element_text(size = 6),
                legend.title = element_text(size = 6),
                legend.key.width = unit(1, unit='cm'),
                legend.key.height = unit(0.25, unit='cm'),
                legend.margin = margin(c(0, 0, -0.4, 0), unit='cm'))
```

```{r}
file_path <- "basketball.csv"
df <- read_csv(file_path)
df %>% head()
```

```{r}
df <- df %>% mutate(
  x = rescale(x, to = c(0,94)),
  y = rescale(y, to = c(-50,0))
)

df %>% head()
```


```{r}
plot <- P_180 +
          # ggplot(df, aes(x=x, y=y)) +
          stat_summary_2d(data=df, aes(x=x, y=y, z=attempts), alpha=0.8, binwidth=c(25/(2*25), 50/(2*47)), fun=sum) +
          # scale_x_continuous(limits=c(-y_range, y_range)) +
          # scale_y_continuous(limits=c(-x_range, x_range)) +
          scale_fill_viridis(option='inferno', end=1, labels=comma, trans='log10') +
          labs(title=sprintf('Heat Map of %s Basketball Shots from NCAA Games', df %>% pull(attempts) %>% sum() %>% comma()),
                subtitle='Starting with the 2013-14 season. Via Sportradar data located in BigQuery',
               fill='# of 2pt/3pt Shot Attempts\nMade From Spot',
               caption = "Max Woolf — minimaxir.com") +
          bb_theme

ggsave('ncaa_count_attempts.png', plot, width=6, height=4)
```

```{r}
plot <- P_180 +
          stat_summary_2d(data=df, aes(x=x, y=y, z=avg_points), alpha=0.8, binwidth=c(25/(2*25), 50/(2*47)), fun=mean, drop=T) +
          scale_fill_viridis(option='inferno', end=1) +
          labs(title=sprintf('Average Points Earned From of %s Basketball Shots from NCAA Games', df %>% pull(attempts) %>% sum() %>% comma()),
                subtitle='Starting with the 2013-14 season. Via Sportradar data located in BigQuery',
               fill='Average Points Earned From Shot Attempts\nMade From Spot',
               caption = "Max Woolf — minimaxir.com") +
          bb_theme

ggsave('ncaa_count_avg_points.png', plot, width=6, height=4)
```


## Half Court

```{r}
file_path_half <- "half_court.csv"
df_half <- read_csv(file_path_half)
df_half %>% head()
```

```{r}
df_half <- df_half %>% mutate(
  x = rescale(x, to = c(0, 47)),
  y = rescale(y, to = c(0, 50)),
  perc_success = successes/attempts
)

df_half %>% head()
```

```{r}
plot <- P_half +
          stat_summary_2d(data=df_half, aes(x=y, y=x, z=attempts), alpha=0.8, bins=100, fun=sum) +
          scale_fill_viridis(option='inferno', end=1, labels=comma) +
          labs(title=sprintf('Heat Map of %s Basketball Shots from NCAA Games', df %>% pull(attempts) %>% sum() %>% comma()),
                subtitle='Starting with the 2013-14 season. Via Sportradar data located in BigQuery',
               fill='# of 2pt/3pt Shot Attempts\nMade From Spot',
               caption = "Max Woolf — minimaxir.com") +
          bb_theme

ggsave('ncaa_count_attempts_half_unlog.png', plot, width=4, height=4)
```

```{r}
plot <- P_half +
          stat_summary_2d(data=df_half, aes(x=y, y=x, z=attempts), alpha=0.8, bins=100, fun=sum) +
          scale_fill_viridis(option='inferno', end=1, labels=comma, trans='log10') +
          labs(title=sprintf('Heat Map of %s Basketball Shots from NCAA Games', df %>% pull(attempts) %>% sum() %>% comma()),
                subtitle='Starting with the 2013-14 season. Via Sportradar data located in BigQuery',
               fill='# of 2pt/3pt Shot Attempts\nMade From Spot',
               caption = "Max Woolf — minimaxir.com") +
          bb_theme

ggsave('ncaa_count_attempts_half_log.png', plot, width=4, height=4)
```

```{r}
mean_thresh <- function(x) {if (length(x) > 3) return (mean(x)) else return (NA) }

plot <- P_half +
          stat_summary_2d(data=df_half, aes(x=y, y=x, z=perc_success), alpha=0.9, bins=100, fun=mean_thresh, drop=T) +
          scale_fill_viridis(option='viridis', end=1, labels=percent, limits=c(0,1)) +
          labs(title=sprintf('Heat Map of %s Basketball Shots from NCAA Games', df %>% pull(attempts) %>% sum() %>% comma()),
                subtitle='Starting with the 2013-14 season. Via Sportradar data located in BigQuery',
               fill='# of 2pt/3pt Shot Attempts\nMade From Spot',
               caption = "Max Woolf — minimaxir.com") +
          bb_theme

ggsave('ncaa_count_attempts_half_perc_success.png', plot, width=4, height=4)
```

```{r}
mean_thresh <- function(x) {if (length(x) > 3) return (mean(x)) else return (NA) }

plot <- P_half +
          stat_summary_2d(data=df_half, aes(x=y, y=x, z=avg_points), alpha=0.9, bins=100, fun=mean) +
          scale_fill_viridis(option='viridis', end=1) +
          labs(title=sprintf('Heat Map of %s Basketball Shots from NCAA Games', df %>% pull(attempts) %>% sum() %>% comma()),
                subtitle='Starting with the 2013-14 season. Via Sportradar data located in BigQuery',
               fill='# of 2pt/3pt Shot Attempts\nMade From Spot',
               caption = "Max Woolf — minimaxir.com") +
          bb_theme

ggsave('ncaa_count_attempts_half_avg_points.png', plot, width=4, height=4)
```

## Half Court, Faceted by Type of Shot

```{r}
file_path_half_types <- "half_types.csv"
df_half_types <- read_csv(file_path_half_types)
df_half_types %>% head()
```

```{r}
df_half_types <- df_half_types %>% mutate(
  x = rescale(x, to = c(0, 47)),
  y = rescale(y, to = c(0, 50)),
  perc_success = successes/attempts
)

df_half_types %>% head()
```

```{r}
plot <- P_half +
          stat_summary_2d(data=df_half_types, aes(x=y, y=x, z=attempts), alpha=0.8, bins=100, fun=sum) +
          scale_fill_viridis(option='inferno', end=1, labels=comma) +
          facet_wrap(~ shot_type, ncol=2) +
          labs(title=sprintf('Heat Map of %s Basketball Shots from NCAA Games', df %>% pull(attempts) %>% sum() %>% comma()),
                subtitle='Starting with the 2013-14 season. Via Sportradar data located in BigQuery',
               fill='# of 2pt/3pt Shot Attempts\nMade From Spot',
               caption = "Max Woolf — minimaxir.com") +
          bb_theme

ggsave('ncaa_count_attempts_half_types_unlog.png', plot, width=4, height=5)
```

```{r}
plot <- P_half +
          stat_summary_2d(data=df_half_types, aes(x=y, y=x, z=attempts), alpha=0.8, bins=100, fun=sum) +
          scale_fill_viridis(option='inferno', end=1, labels=comma, trans='log10') +
          facet_wrap(~ shot_type, ncol=2) +
          labs(title=sprintf('Heat Map of %s Basketball Shots from NCAA Games', df %>% pull(attempts) %>% sum() %>% comma()),
                subtitle='Starting with the 2013-14 season. Via Sportradar data located in BigQuery',
               fill='# of 2pt/3pt Shot Attempts\nMade From Spot',
               caption = "Max Woolf — minimaxir.com") +
          bb_theme

ggsave('ncaa_count_attempts_half_types_log.png', plot, width=3, height=5)
```

```{r}
plot <- P_half +
          stat_summary_2d(data=df_half_types, aes(x=y, y=x, z=perc_success), alpha=0.9, bins=100, fun=mean_thresh, drop=T) +
          scale_fill_viridis(option='viridis', end=1, labels=percent, limits=c(0,1)) +
          facet_wrap(~ shot_type, ncol=2) +
          labs(title=sprintf('Heat Map of %s Basketball Shots from NCAA Games', df %>% pull(attempts) %>% sum() %>% comma()),
                subtitle='Starting with the 2013-14 season. Via Sportradar data located in BigQuery',
               fill='# of 2pt/3pt Shot Attempts\nMade From Spot',
               caption = "Max Woolf — minimaxir.com") +
          bb_theme

ggsave('ncaa_count_attempts_half_types_perc_success.png', plot, width=3, height=5)
```

```{r}
plot <- P_half +
          stat_summary_2d(data=df_half_types, aes(x=y, y=x, z=avg_points), alpha=0.9, bins=100, fun=mean) +
          scale_fill_viridis(option='viridis', end=1) +
          facet_wrap(~ shot_type, ncol=2) +
          labs(title=sprintf('Heat Map of %s Basketball Shots from NCAA Games', df %>% pull(attempts) %>% sum() %>% comma()),
                subtitle='Starting with the 2013-14 season. Via Sportradar data located in BigQuery',
               fill='# of 2pt/3pt Shot Attempts\nMade From Spot',
               caption = "Max Woolf — minimaxir.com") +
          bb_theme

ggsave('ncaa_count_attempts_half_types_avg_points.png', plot, width=3, height=5)
```

```{r}
file_path_half_types <- "half_types.csv"
df_half_types <- read_csv(file_path_half_types)
df_half_types %>% head()
```

```{r}
df_half_types <- df_half_types %>% mutate(
  x = rescale(x, to = c(0, 47)),
  y = rescale(y, to = c(0, 50)),
  perc_success = successes/attempts
)

df_half_types %>% head()
```

```{r}
plot <- P_half +
          stat_summary_2d(data=df_half_types, aes(x=y, y=x, z=attempts), alpha=0.8, bins=100, fun=sum) +
          scale_fill_viridis(option='inferno', end=1, labels=comma) +
          facet_wrap(~ shot_type, ncol=2) +
          labs(title=sprintf('Heat Map of %s Basketball Shots from NCAA Games', df %>% pull(attempts) %>% sum() %>% comma()),
                subtitle='Starting with the 2013-14 season. Via Sportradar data located in BigQuery',
               fill='# of 2pt/3pt Shot Attempts\nMade From Spot',
               caption = "Max Woolf — minimaxir.com") +
          bb_theme

ggsave('ncaa_count_attempts_half_types_unlog.png', plot, width=4, height=5)
```

```{r}
plot <- P_half +
          stat_summary_2d(data=df_half_types, aes(x=y, y=x, z=attempts), alpha=0.8, bins=100, fun=sum) +
          scale_fill_viridis(option='inferno', end=1, labels=comma, trans='log10') +
          facet_wrap(~ shot_type, ncol=2) +
          labs(title=sprintf('Heat Map of %s Basketball Shots from NCAA Games', df %>% pull(attempts) %>% sum() %>% comma()),
                subtitle='Starting with the 2013-14 season. Via Sportradar data located in BigQuery',
               fill='# of 2pt/3pt Shot Attempts\nMade From Spot',
               caption = "Max Woolf — minimaxir.com") +
          bb_theme

ggsave('ncaa_count_attempts_half_types_log.png', plot, width=3, height=5)
```

```{r}
plot <- P_half +
          stat_summary_2d(data=df_half_types, aes(x=y, y=x, z=perc_success), alpha=0.9, bins=100, fun=mean_thresh, drop=T) +
          scale_fill_viridis(option='viridis', end=1, labels=percent, limits=c(0,1)) +
          facet_wrap(~ shot_type, ncol=2) +
          labs(title=sprintf('Heat Map of %s Basketball Shots from NCAA Games', df %>% pull(attempts) %>% sum() %>% comma()),
                subtitle='Starting with the 2013-14 season. Via Sportradar data located in BigQuery',
               fill='# of 2pt/3pt Shot Attempts\nMade From Spot',
               caption = "Max Woolf — minimaxir.com") +
          bb_theme

ggsave('ncaa_count_attempts_half_types_perc_success.png', plot, width=3, height=5)
```

```{r}
plot <- P_half +
          stat_summary_2d(data=df_half_types, aes(x=y, y=x, z=avg_points), alpha=0.9, bins=100, fun=mean) +
          scale_fill_viridis(option='viridis', end=1) +
          facet_wrap(~ shot_type, ncol=2) +
          labs(title=sprintf('Heat Map of %s Basketball Shots from NCAA Games', df %>% pull(attempts) %>% sum() %>% comma()),
                subtitle='Starting with the 2013-14 season. Via Sportradar data located in BigQuery',
               fill='# of 2pt/3pt Shot Attempts\nMade From Spot',
               caption = "Max Woolf — minimaxir.com") +
          bb_theme

ggsave('ncaa_count_attempts_half_types_avg_points.png', plot, width=3, height=5)
```
## Half Court, Faceted by 10 Minute Time Buckets.

```{r}
file_path_half_interval <- "half_interval.csv"
df_half_interval <- read_csv(file_path_half_interval)
df_half_interval %>% head()
```

```{r}
df_half_interval <- df_half_interval %>% mutate(
  x = rescale(x, to = c(0, 47)),
  y = rescale(y, to = c(0, 50)),
  perc_success = successes/attempts
)

df_half_interval %>% head()
```

```{r}
plot <- P_half +
          stat_summary_2d(data=df_half_interval, aes(x=y, y=x, z=attempts), alpha=0.8, bins=100, fun=sum) +
          scale_fill_viridis(option='inferno', end=1, labels=comma) +
          facet_wrap(~ min_interval, ncol=4) +
          labs(title=sprintf('Heat Map of %s Basketball Shots from NCAA Games', df %>% pull(attempts) %>% sum() %>% comma()),
                subtitle='Starting with the 2013-14 season. Via Sportradar data located in BigQuery',
               fill='# of 2pt/3pt Shot Attempts\nMade From Spot',
               caption = "Max Woolf — minimaxir.com") +
          bb_theme

ggsave('ncaa_count_attempts_half_interval_unlog.png', plot, width=4, height=4)
```

```{r}
plot <- P_half +
          stat_summary_2d(data=df_half_interval, aes(x=y, y=x, z=attempts), alpha=0.8, bins=100, fun=sum) +
          scale_fill_viridis(option='inferno', end=1, labels=comma, trans='log10') +
          facet_wrap(~ min_interval, ncol=4) +
          labs(title=sprintf('Heat Map of %s Basketball Shots from NCAA Games', df %>% pull(attempts) %>% sum() %>% comma()),
                subtitle='Starting with the 2013-14 season. Via Sportradar data located in BigQuery',
               fill='# of 2pt/3pt Shot Attempts\nMade From Spot',
               caption = "Max Woolf — minimaxir.com") +
          bb_theme

ggsave('ncaa_count_attempts_half_interval_log.png', plot, width=4, height=4)
```

```{r}
plot <- P_half +
          stat_summary_2d(data=df_half_interval, aes(x=y, y=x, z=perc_success), alpha=0.9, bins=100, fun=mean_thresh, drop=T) +
          scale_fill_viridis(option='viridis', end=1, labels=percent, limits=c(0,1)) +
          facet_wrap(~ min_interval, ncol=4) +
          labs(title=sprintf('Heat Map of %s Basketball Shots from NCAA Games', df %>% pull(attempts) %>% sum() %>% comma()),
                subtitle='Starting with the 2013-14 season. Via Sportradar data located in BigQuery',
               fill='# of 2pt/3pt Shot Attempts\nMade From Spot',
               caption = "Max Woolf — minimaxir.com") +
          bb_theme

ggsave('ncaa_count_attempts_half_interval_perc_success.png', plot, width=4, height=4)
```

```{r}
plot <- P_half +
          stat_summary_2d(data=df_half_interval, aes(x=y, y=x, z=avg_points), alpha=0.9, bins=100, fun=mean) +
          scale_fill_viridis(option='viridis', end=1) +
          facet_wrap(~ min_interval, ncol=4) +
          labs(title=sprintf('Heat Map of %s Basketball Shots from NCAA Games', df %>% pull(attempts) %>% sum() %>% comma()),
                subtitle='Starting with the 2013-14 season. Via Sportradar data located in BigQuery',
               fill='# of 2pt/3pt Shot Attempts\nMade From Spot',
               caption = "Max Woolf — minimaxir.com") +
          bb_theme

ggsave('ncaa_count_attempts_half_types_avg_points.png', plot, width=4, height=4)
```

## Half Court, by Point Delta at Time of Shot

```{r}
file_path_half_score <- "half_score.csv"
df_half_score <- read_csv(file_path_half_score)
df_half_score %>% head()
```

```{r}
score_levels <- c('<-20', '-20 — -11', '-10 — -1', '0', '1 — 10', '11 — 20', '>20')

df_half_score <- df_half_score %>% mutate(
  x = rescale(x, to = c(0, 47)),
  y = rescale(y, to = c(0, 50)),
  perc_success = successes/attempts,
  score_delta_interval = factor(score_delta_interval, levels = score_levels)
)

df_half_score %>% head()
```

```{r}
plot <- P_half +
          stat_summary_2d(data=df_half_score, aes(x=y, y=x, z=attempts), alpha=0.8, bins=25, fun=sum) +
          scale_fill_viridis(option='inferno', end=1, labels=comma) +
          facet_grid(shot_type ~ score_delta_interval) +
          labs(title=sprintf('Heat Map of %s Basketball Shots from NCAA Games', df %>% pull(attempts) %>% sum() %>% comma()),
                subtitle='Starting with the 2013-14 season. Via Sportradar data located in BigQuery',
               fill='# of 2pt/3pt Shot Attempts\nMade From Spot',
               caption = "Max Woolf — minimaxir.com") +
          bb_theme

ggsave('ncaa_count_attempts_half_score_unlog.png', plot, width=4, height=4)
```

```{r}
plot <- P_half +
          stat_summary_2d(data=df_half_score, aes(x=y, y=x, z=attempts), alpha=0.8, bins=25, fun=sum) +
          scale_fill_viridis(option='inferno', end=1, labels=comma, trans='log10') +
          facet_grid(shot_type ~ score_delta_interval) +
          labs(title=sprintf('Heat Map of %s Basketball Shots from NCAA Games', df %>% pull(attempts) %>% sum() %>% comma()),
                subtitle='Starting with the 2013-14 season. Via Sportradar data located in BigQuery',
               fill='# of 2pt/3pt Shot Attempts\nMade From Spot',
               caption = "Max Woolf — minimaxir.com") +
          bb_theme

ggsave('ncaa_count_attempts_half_score_log.png', plot, width=4, height=4)
```

```{r}
plot <- P_half +
          stat_summary_2d(data=df_half_score, aes(x=y, y=x, z=perc_success), alpha=0.9, bins=25, fun=mean_thresh, drop=T) +
          scale_fill_viridis(option='viridis', end=1, labels=percent, limits=c(0,1)) +
          facet_grid(shot_type ~ score_delta_interval) +
          labs(title=sprintf('Heat Map of %s Basketball Shots from NCAA Games', df %>% pull(attempts) %>% sum() %>% comma()),
                subtitle='Starting with the 2013-14 season. Via Sportradar data located in BigQuery',
               fill='# of 2pt/3pt Shot Attempts\nMade From Spot',
               caption = "Max Woolf — minimaxir.com") +
          bb_theme

ggsave('ncaa_count_attempts_half_score_perc_success.png', plot, width=4, height=4)
```

```{r}
plot <- P_half +
          stat_summary_2d(data=df_half_score, aes(x=y, y=x, z=avg_points), alpha=0.9, bins=25, fun=mean) +
          scale_fill_viridis(option='viridis', end=1) +
          facet_grid(shot_type ~ score_delta_interval) +
          labs(title=sprintf('Heat Map of %s Basketball Shots from NCAA Games', df %>% pull(attempts) %>% sum() %>% comma()),
                subtitle='Starting with the 2013-14 season. Via Sportradar data located in BigQuery',
               fill='# of 2pt/3pt Shot Attempts\nMade From Spot',
               caption = "Max Woolf — minimaxir.com") +
          bb_theme

ggsave('ncaa_count_attempts_half_score_avg_points.png', plot, width=4, height=4)
```


## Heat Map of Elapsed Time vs. Success

## Heat Map of Score Delta vs. Success

# LICENSE

The MIT License (MIT)

Copyright (c) 2018 Max Woolf

Permission is hereby granted, free of charge, to any person obtaining a copy of this software and associated documentation files (the "Software"), to deal in the Software without restriction, including without limitation the rights to use, copy, modify, merge, publish, distribute, sublicense, and/or sell copies of the Software, and to permit persons to whom the Software is furnished to do so, subject to the following conditions:

The above copyright notice and this permission notice shall be included in all copies or substantial portions of the Software.

THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE SOFTWARE.